### 2020-08-25 3-Dissertation/6-error.tex
Updated dissertation document according to Dr. Watson suggestions, included MQSI package code in an Appendix.

The theoretical results constructed in Section \ref{sec:theory} for
(piecewise) linear interpolation are promising and apply directly to
Delaunay interpolation, however they are difficult to interpret in
context with approximation algorithms that do not have similar known
uniform error bounds. For that reason, an analytic function is used to
measure the error of a piecewise linear interpolant (Delaunay) and a
piecewise linear regressor (the MLP) when provided an increasing
amount of data with varying levels of random noise. Only
Delaunay and the MLP are considered in this demonstration because
all other mentioned techniques are not strictly piecewise linear
approximations.

@@

In addition to the figures displaying approximation results for each
data set, scatter plots of predicted versus actual values
  and tables of accompanying numerical results including
  timings and quartiles of prediction error are located in the
Appendix (Section \ref{sec:appendix}). All of the test data sets
capture underlying functions that are almost certainly stochastic. As
described in Section \ref{sec:introduction}, regression techniques
appear most appropriate for these problems. However, typically data
grows exponentially more sparse with increasing dimension. Given that
sparse data regressors tend towards interpolation and, as demonstrated
in Section \ref{sec:analytic}, interpolants produce similar (if not
identical) results, it is presumed that interpolants are equally
viable approximation techniques on these problems.

>>>>

The theoretical results constructed in Chapter \ref{ch:error} for
(piecewise) linear interpolation are promising and apply directly to
Delaunay interpolation, however they are difficult to interpret in
context with approximation algorithms that do not have similar known
uniform error bounds. For that reason, an analytic function is used to
measure the error of a piecewise linear interpolant (Delaunay) and a
piecewise linear regressor (the MLP) when provided an increasing
amount of data with varying levels of random noise. Only
Delaunay and the MLP are considered in this demonstration because
all other mentioned techniques are not strictly piecewise linear
approximations.

@@

In addition to the figures displaying approximation results for each
data set, scatter plots of predicted versus actual values
  and tables of accompanying numerical results including
  timings and quartiles of prediction error are located in the
Appendix (Section \ref{app:error}). All of the test data sets
capture underlying functions that are almost certainly stochastic. As
described in Chapter \ref{ch:algs}, regression techniques
appear most appropriate for these problems. However, typically data
grows exponentially more sparse with increasing dimension. Given that
sparse data regressors tend towards interpolation and, as demonstrated
in Section \ref{sec:analytic}, interpolants produce similar (if not
identical) results, it is presumed that interpolants are equally
viable approximation techniques on these problems.
